Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
more text, editing and references added

Commercially available mungbean cultivars in Australia lack suficient resistance to be used soley as a management strategy to avoid yield losses.
Quantitative disease resistance has been shown in a few cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required.

>>>>

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used soley as a management strategy for mitigating yield losses.
Quantitative disease resistance has been observed in breeding lines [@Pandey2018; @Chankaew2013] and mungbean cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required[@Kelly2017a].
